---
title: "`r params$title`"
date: "`r format(Sys.time(), '%d/%m/%Y')`"
format: 
  html:
    theme: cosmo
    version: 5
params:
  data_processed: NA
  data_raw: NA
  data_type: NA
  title: NA
  translations: NA
  indicator_tab: NA
  global_form: NA
  womens_form: NA
  language: NA
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, error=FALSE,message = FALSE)

library(tidyverse)
library(openxlsx)
library(gt)
library(gtsummary)

#devtools::install_github("sdumble1/ODKTools")
#library(ODKTools)

source("functions/functions.R")
source("functions/report_functions.R")

# params <- NULL
# 
#      params <- list(
#        title = paste0("Senegal", " Summary Report"),
#        data_processed = NA,
#        data_raw = data1,
#        language = input$language,
#        #summary_vars = input$summary_vars,
# #        data_type = "raw",
#       translations = report_translations,
#       indicator_tab = indicator_tab,
#       global_form = form_schema_ext(fid=Sys.getenv("form_id")),
#       womens_form = form_schema_ext(fid=Sys.getenv("women_form_id"))
#     )

#set up forms and langauage
global_form <- params$global_form
womens_form <- params$womens_form
language_trans <- params$language

if(params$data_type == "raw"){

  #set data frames
  data_list <- params$data_raw
  
  #global
  global <-  data_list$global$full_data
  global <- number_fix(global) #fix to numeric those that should be as such
  
    #fix column names
  cols_global <- data.frame(ruodk_name = colnames(global))
  cols_global_ruodk <- data.frame(ruodk_name = global_form$ruodk_name,
                                  short_name = global_form$name)
  cols_global <- cols_global%>%
    left_join(cols_global_ruodk)%>%
    mutate(short_name = ifelse(is.na(short_name), ruodk_name, short_name))
  
  colnames(global) <- cols_global$short_name
  print(colnames(global))
    #merge labels for variables
  global <- merge_labels_clean(global, global_form, language_trans)
  
  #women
  womens <-  data_list$women$full_data
  womens <- number_fix(womens) #fix numeric variables
    #fix column names
  cols_women <- data.frame(ruodk_name = colnames(womens))
  cols_women_ruodk <- data.frame(ruodk_name = womens_form$ruodk_name,
                                  short_name = womens_form$name)
  cols_women <- cols_women%>%
    left_join(cols_women_ruodk)%>%
    mutate(short_name = ifelse(is.na(short_name), ruodk_name, short_name))
  
  colnames(womens) <- cols_women$short_name
  
  #redo assets - ignore labels
  wom_assets <- womens%>%select(id,ends_with("own"))
  #merge in clean labels for womens data
  womens <- merge_labels_clean(womens, womens_form, language_trans)
  #join asset vars back
  womens <- womens%>%select(-ends_with("own"))%>%
    left_join(wom_assets)
  
  ##EXCLUDE DUPLICATES
  global <- global%>%
    group_by(household_id)%>%
    mutate(n = n())%>%
    filter(n==1)
  
  womens <- womens%>%
    group_by(household_id)%>%
    mutate(n = n())%>%
    filter(n==1)
  
  #global - join womens age
  global <- global%>%left_join(womens%>%select(household_id,respondentage))
  
  #crops
  crops <- data_list$global$repeats$survey_grp_section_crop_productivity_crop_repeat
  crops <- number_fix(crops) #fix to numeric
    #fix column names
  cols_crops <- data.frame(ruodk_name = colnames(crops))
  crop_form <- global_form%>%filter(str_detect(ruodk_name,"crop_repeat"))%>%filter(name!="crop_repeat")%>%filter(type!="structure")
  
  colnames(crops) <- c(crop_form$name, "id", "submissions_id", "odata_context")
  
  #merge in crop label in relevant language 
  crops <- merge_crops_label(crops, global_form, language_trans)
  #exclude other crops
  crops <- crops%>%filter(!is.na(label_lang) & label_lang!="")
  crops <- crops%>%filter(!str_detect(crop_label, "\\:"))
  
  #relevel missing levels in cosumed and sold props for crops
  crops$crop_consumed_prop[is.na(crops$crop_consumed_prop) & crops$crop_use=="eat"] <- levels(crops$crop_consumed_prop)[1]
  crops$crop_consumed_prop[is.na(crops$crop_consumed_prop)] <- levels(crops$crop_consumed_prop)[6]
  
  crops$crop_sold_prop[is.na(crops$crop_sold_prop) & crops$crop_use=="sell"] <- levels(crops$crop_sold_prop)[1]
  crops$crop_sold_prop[is.na(crops$crop_sold_prop)] <- levels(crops$crop_sold_prop)[6]
  
  #off_farm
  #fix column names
  off_farm <- data_list$global$repeats$survey_grp_offfarm_income_grp_section_off_farm_income_offfarm_income_repeat
  cols_off_farm <- data.frame(ruodk_name = colnames(off_farm))
  off_farm_form <- global_form%>%filter(str_detect(ruodk_name, "offfarm_income_repeat"))%>%
    filter(name!="offfarm_income_repeat")%>%filter(type!="structure")
  
  colnames(off_farm) <- c(off_farm_form$name, "id", "submissions_id", "odata_context")
  
  #filter missing income names
  off_farm <- off_farm%>%filter(!is.na(offfarm_income_name))
  
  if("livestock_owners" %in% colnames(global)){
  #livestock
  livestock <- data_list$global$repeats$survey_grp_section_livestock_livestock_repeat
  livestock <- number_fix(livestock) #fix to numeric
    #fix column names
  cols_ls <- data.frame(ruodk_name = colnames(livestock))
  ls_form <- global_form%>%filter(str_detect(ruodk_name,"livestock_repeat"))%>%filter(name!="livestock_repeat")%>%filter(type!="structure")
  
  colnames(livestock) <- c(ls_form$name, "id", "submissions_id", "odata_context")
  
  livestock <- merge_livestock_label(livestock, global_form, language_trans)
  }
  
  #indicators
  indicators <- data_list$indicators


}else{

  data_list <- params$data_processed
  
  #global
  #merge clean labels
  global <-  params$data_processed$global%>%left_join(data_list$women%>%select(household_id,respondentage))
  #global <- merge_labels_clean(global, global_form, language_trans)
  
  #women
  #merge clean labels except assets
  womens <-  params$data_processed$women
  # wom_assets <- womens%>%select(household_id,ends_with("own"))
  # womens <- merge_labels_clean(womens, womens_form, language_trans)
  # womens <- womens%>%select(-ends_with("own"))%>%
  #   left_join(wom_assets)
  
  #crops
  crops <- params$data_processed$crops
  #crops <- merge_crops_label(crops, global_form, language_trans)
  #exclude other crops
  crops <- crops%>%filter(!is.na(label_lang) & label_lang!="")
  crops <- crops%>%filter(!str_detect(crop_label, "\\:"))
  
  if("livestock_owners" %in% colnames(global)){
  livestock <- params$data_processed$livestock
  }
  
  #off_farm
  off_farm <- params$data_processed$off_farm%>%filter(!is.na(offfarm_income_name))
  
  indicators <- params$data_processed$indicators

}

indicator_tab <- params$indicator_tab

indicators <- data.frame(indicators)

min_date <- min(as_date(global$interview_date))
max_date <- max(as_date(global$interview_date))
```

## `r params$translations[params$translations$english=="Survey Summary", language_trans]`

`r md(paste0("**",params$translations[params$translations$english=="Data Collection Dates:", language_trans],"**")) ` : `r paste0(min_date, " - ", max_date)`

```{r}
data.frame(
    Form = params$translations[params$translations$type=="label" & params$translations$indicator=="Survey Summary", language_trans],
    N = c(
      nrow(global),
      nrow(womens),
      sum(global$household_id%in%womens$household_id),
      sum(!global$household_id%in%womens$household_id),
      sum(!womens$household_id%in%global$household_id)
    )
  )%>%
  gt()%>%
  cols_label(
    Form = params$translations[params$translations$english == "Form", language_trans]
  )
```

## `r params$translations[params$translations$english=="Sample Demographics", language_trans]`

```{r}
global%>%
tbl_summary(
  include = c(loc1_name, participant_sex, participant_age, respondentage, education_level),
  label = list(
    #loc ~ loc_type,
    participant_sex ~ params$translations[params$translations$english=="Respondent Sex", language_trans],
    participant_age ~ params$translations[params$translations$english=="Respondent Age", language_trans],
    respondentage ~ params$translations[params$translations$english=="Women's Form Respondent Age", language_trans],
    education_level ~ params$translations[params$translations$english=="Education (Household Head)", language_trans]
  ),
  missing = "no"
)%>%
  modify_header(label ~  
                  md(paste0("**",params$translations[params$translations$english=="Characteristic",
                                              language_trans],"**")))
```


## Indicator Summary

```{r}
indicator_tab <- indicator_tab%>%filter(Available == 1)

for(i in 1:nrow(indicator_tab)){

  if(indicator_tab$summary[i]=="asis"){

    indicator_tab$value[i] <- scales::percent(indicators[1,indicator_tab$indicator[i]],accuracy = 0.1)

  }

    if(indicator_tab$summary[i]=="median"){

    indicator_tab$value[i] <- round(median(indicators[,indicator_tab$indicator[i]],na.rm = TRUE),2)



    }

     if(indicator_tab$summary[i]=="median_prop"){

    indicator_tab$value[i] <-
      paste0(scales::percent(median(indicators[,indicator_tab$indicator[i]],na.rm = TRUE),accuracy = 0.1))



  }

  if(indicator_tab$summary[i] == "prop"){

    if(indicator_tab$binary[i] == 1){

    indicator_tab$value[i] <- scales::percent(mean(indicators[,indicator_tab$indicator[i]],na.rm=TRUE),accuracy = 0.1)

    }

    if(indicator_tab$indicator[i] == "I_HI_n_income_sources"){

    indicator_tab$value[i] <- scales::percent(mean(indicators[,indicator_tab$indicator[i]]>=2,na.rm=TRUE),accuracy = 0.1)

    }

        if(str_detect(indicator_tab$indicator[i], "I_VCC")){

    results <- indicators[,indicator_tab$indicator[i]]


    results <- case_when(
    results%in%c(levels(results)[4],levels(results)[5]) ~ 1,
    results == levels(results)[6] | is.na(results) ~ NA,
    .default = 0)
  

    indicator_tab$value[i] <- scales::percent(mean(results,na.rm=TRUE),accuracy = 0.1)

    }


  }
}

xx <- indicator_tab[,c("objective", language_trans, "value")]

colnames(xx) <- c("objective", params$translations[params$translations$indicator=="Indicators", language_trans])

gt(xx, groupname_col = "objective")
```


\pagebreak

## `r params$translations[params$translations$english=="PO.1 Productivity", language_trans]`

`r md(paste0("**",params$translations[params$translations$english=="Objective Definition", language_trans],"**"))` : `r params$translations[params$translations$element=="definition1", language_trans]`

### `r params$translations[params$translations$english=="Crop Production", language_trans]`

```{r}
crop_labels <- params$translations%>%
  filter(indicator=="Crop Production")

crop_tab <- crops%>%
  group_by(label_lang)%>%
  summarise(n = n(),
            perc = n/nrow(global)*100,
            area = mean(crop_area_ha,na.rm=TRUE),
            yield = mean(crop_yield_kg,na.rm=TRUE),
            prod = mean(crop_yield_kg_ha,na.rm=TRUE))%>%
  arrange(desc(n))%>%
  mutate(N_perc = paste0(n, " (", formatC(round(perc,1),format='f',digits = 1), "%)"))%>%
  select(label_lang, N_perc, area,   yield, prod)

crop_tab%>%
  gt()%>%
  cols_label(
    label_lang = crop_labels[1,language_trans],
    N_perc = crop_labels[2,language_trans],
    area = crop_labels[3,language_trans],
    yield = crop_labels[4,language_trans],
    prod = crop_labels[5,language_trans]
  )%>%
  fmt_number(columns = 3,decimals = 2)%>%
  fmt_number(columns = c(4,5), decimals = 0)%>%
  fmt_missing(missing_text = "")%>%
  gt::tab_footnote(footnote = crop_labels[6,language_trans])
```

\pagebreak

`r md(paste0("**",params$translations[params$translations$english=="Number of crops grown in a farm", language_trans],"**"))`

```{r, fig.height=6}
indicators%>%
  select(household_id,I_P_total_crops,I_P_total_important_crops)%>%
  pivot_longer(cols = -household_id)%>%
  mutate(name = ifelse(name=="I_P_total_crops", params$translations[params$translations$english=="Total", language_trans],
                       params$translations[params$translations$english=="Important only", language_trans])) -> crop_nums
  # group_by(name, value)%>%
  # summarise(n = n())%>%
  # filter(!is.na(value))%>%
  # mutate(value = factor(value, levels = seq(from = min(value, na.rm = T), to=max(value, na.rm = TRUE), by = 1)))
  
crop_nums%>%
  ggplot(aes(y = value))+
  geom_bar(fill = "#E0EABE", colour = "black")+
  stat_count(geom="label", aes(label = ..count..), size = 3)+
  facet_wrap(~name)+
  labs(y = params$translations[params$translations$english=="Number of crops grown", language_trans],
       x = params$translations[params$translations$english=="Number of Households", language_trans][1])+
  theme_bw()+
  scale_y_reverse(breaks = 0:max(crop_nums$value,na.rm = T))
```

\pagebreak

`r md(paste0("**",params$translations[params$translations$english=="Area of main crops (Ha)", language_trans],"**"))`

`r language_switch(language = language_trans, element_name = "extra_text9", language_file = params$translations)`

```{r, fig.height=8}
maxArea <- max(crops$crop_area_ha,na.rm=TRUE)/2.5

crops%>%
  group_by(label_lang)%>%
  mutate(n = n())%>%
  filter(n >= 5)%>%# DEFINITION TBD - MIGHT NEED FILTER ON OUTLIERS
  mutate(label_lang = paste0(label_lang, " (n=",n,")"))%>%
  ggplot(aes(y = reorder(label_lang,n), x = crop_area_ha, fill = reorder(label_lang,n) ))+
  geom_boxplot(outliers = FALSE)+
  geom_jitter(alpha = 0.5)+
  labs(x = params$translations[params$translations$english=="Crop area (Ha)", language_trans],
       y = params$translations[params$translations$english=="Crop", language_trans])+
  theme_bw()+
  theme(legend.position = "none")+
  scale_fill_brewer(palette = "Set3")+
  scale_x_continuous(n.breaks = round(maxArea))
```

\pagebreak

`r md(paste0("**",params$translations[params$translations$english=="Crop Yields (Kg/Ha)", language_trans],"**"))`

`r language_switch(language = language_trans, element_name = "extra_text10", language_file = params$translations)`

```{r, fig.height = 8}
crops%>%
  group_by(label_lang)%>%
  mutate(n = n())%>%
  filter(n>=5)%>%
  mutate(label_lang = paste0(label_lang, " (n=",n,")"))%>%
  ggplot(aes(y = reorder(label_lang,n), x = crop_yield_kg_ha, fill = reorder(label_lang,n) ))+
  geom_boxplot(outliers = FALSE)+
  geom_jitter(alpha = 0.5)+
  labs(x = params$translations[params$translations$english=="Crop Productivity (Kg/Ha)", language_trans],
       y = params$translations[params$translations$english=="Crop", language_trans])+
  theme_bw()+
  theme(legend.position = "none")+
  scale_fill_brewer(palette = "Set3")+
  scale_x_continuous(n.breaks = 10)
```

```{r, results = 'asis'}
if("livestock_owners" %in% colnames(global)){
  cat('\\pagebreak')
}
```


### `r ifelse("livestock_owners" %in% colnames(global), language_switch(language = language_trans, element_name = "header28", language_file = params$translations), '')`

```{r}
if("livestock_owners" %in% colnames(global)){
 
owns <- global%>%
    select(starts_with("livestock_heads_"))%>%
    ungroup()%>%
    summarise_at(vars(starts_with("livestock_heads_")), function(x) paste0(sum(!is.na(x)), " (", formatC(round(mean(!is.na(x))*100,1),format='f',digits = 1), "%)"))%>%
    pivot_longer(cols = everything(),values_to = "ownership")

heads <- global%>%
    select(starts_with("livestock_heads_"))%>%
    ungroup()%>%
    mutate_at(vars(starts_with("livestock_heads_")), function(x) ifelse(x==-999, NA, x))%>%
    summarise_at(vars(starts_with("livestock_heads_")), function(x) median(x, na.rm = TRUE))%>%
    pivot_longer(cols = everything(),values_to = "heads")

livestock_summary <- left_join(owns,heads)  %>%
  mutate(name = str_extract(name, "[^_]+$"))%>%
  filter(name != "lstk" & name!="buffalo")

livestock_summary <- livestock_summary%>%
  left_join(livestock%>%
  select(-starts_with("ls_"))%>%
  mutate(livestock_id = case_when(
    livestock_id=="donkey" ~ "donkeys",
    livestock_id=="bees" ~ "beehives",
    livestock_id=="rabbit" ~ "rabbits",
    .default = livestock_id
  ))%>%
  group_by(livestock_id)%>%
  summarise_at(
    vars(livestock_bought, livestock_live_birth, livestock_sold, livestock_died, livestock_sale_income), function(x) median(x, na.rm = TRUE)
  )%>%
  filter(!str_detect(livestock_id, "other")), by = c("name" = "livestock_id"))

livestock_summary <- livestock_summary %>%
  mutate(n = str_extract(ownership, "^[^\\(]+"))%>%
  arrange(desc(as.numeric(n)))%>%
  select(-n)%>%
  left_join(params$translations[,c("indicator",language_trans)], by = c("name" = "indicator"))

colnames(livestock_summary) <-
  c("name", params$translations[params$translations$indicator=="livestock", language_trans])

livestock_summary%>%
  select(9, everything())%>%
  select(-name)%>%
  gt()%>%
  fmt_number(columns = 3:7,decimals = 0)%>%
  fmt_missing(missing_text = "")
}
```

```{r, fig.height=6}
if("livestock_owners" %in% colnames(global)){

indicators%>%
  select(household_id,I_P_total_livestock,I_P_total_important_livestocks)%>%
  pivot_longer(cols = -household_id)%>%
  mutate(name = ifelse(name=="I_P_total_livestock", params$translations[params$translations$english=="Total", language_trans],
                       params$translations[params$translations$english=="Important only", language_trans])) -> ls_nums
  # group_by(name, value)%>%
  # summarise(n = n())%>%
  # filter(!is.na(value))%>%
  # mutate(value = factor(value, levels = seq(from = min(value, na.rm = T), to=max(value, na.rm = TRUE), by = 1)))
  
ls_nums%>%
  ggplot(aes(y = value))+
  geom_bar(fill = "#E0EABE", colour = "black")+
  stat_count(geom="label", aes(label = ..count..), size = 3)+
  facet_wrap(~name)+
  labs(y = params$translations[params$translations$english=="Number of livestock species kept", language_trans],
       x = params$translations[params$translations$english=="Number of Households", language_trans][1])+
  theme_bw()+
  scale_y_reverse(breaks = 0:max(crop_nums$value,na.rm = T))

}
```

\pagebreak

## `r params$translations[params$translations$english=="PO.2 Womens Empowerment", language_trans]`

`r md(paste0("**",params$translations[params$translations$english=="Objective Definition", language_trans],"**"))` : `r params$translations[params$translations$element=="definition2", language_trans]`

`r md(paste0("**",params$translations[params$translations$english=="Proportion of households where women have equal/more influence or voice about...", language_trans][1],"**"))`

```{r}
VCC <- indicators%>%
  select(household_id,I_VCC1:I_VCC6)

VCC%>%
    mutate_at(vars(starts_with("I_VCC")), function(x) case_when(
    x%in%c(levels(x)[4],levels(x)[5]) ~ 1,
    x == levels(x)[6] ~ NA,
    .default = 0
  ))%>%
  pivot_longer(cols = -household_id)%>%
  group_by(name)%>%
  summarise(
    N = sum(!is.na(value)),
    n = sum(value,na.rm = TRUE),
    perc = n/N
  )%>%
  mutate(name = case_when(
    name == "I_VCC1" ~ paste0(params$translations[params$translations$english=="Crops grown for food", language_trans], " (n=",N,")"),
    name == "I_VCC2" ~ paste0(params$translations[params$translations$english=="Crops grown for the market", language_trans]," (n=",N,")"),
    name == "I_VCC3" ~ paste0(params$translations[params$translations$english=="Expenditure of household savings", language_trans]," (", "n=",N,")"),
    name == "I_VCC4" ~ paste0(params$translations[params$translations$english=="Choose how to spend their own income", language_trans]," (", "n=",N,")"),
    name == "I_VCC5" ~ paste0(params$translations[params$translations$english=="Choose what to sell in the market", language_trans]," (", "n=",N,")"),
    name == "I_VCC6" ~ paste0(params$translations[params$translations$english=="Participate in community committees – specifically can they choose how they allocate time to community groups, farm work, etc.", language_trans]," (n = ",N,")")
  ))%>%
  mutate(name = str_wrap(name,35))%>%
  ggplot(aes(y = name, x = perc))+
  geom_col(fill = "#F39F5D", colour = "black")+
  geom_label(aes(label = scales::percent(perc,accuracy = 0.1)))+
  scale_x_continuous(labels = scales::percent, limits = c(0,1))+
  labs(x = NULL,
       title = str_wrap(params$translations[params$translations$indicator=="I_VCC" & params$translations$type=="title", language_trans],50),
       y = NULL)+
  theme_bw()
```

\pagebreak

`r md(paste0("**",params$translations[params$translations$english=="A-WEAI - Access to productive capital", language_trans],"**"))`

```{r}
asset_labels <- params$translations%>%filter(indicator=="I_AWEAI_asset")

assets <- womens%>%
  select(household_id,ends_with("own"))%>%
  mutate_at(vars(ends_with("own")), function(x)
            case_when(
              x %in% c(1,2) ~ asset_labels[asset_labels$english=="Joint/Sole ownership", language_trans],
              x %in% c(3) ~ asset_labels[asset_labels$english=="Owned by other household member", language_trans],
              .default = asset_labels[asset_labels$english=="Unowned", language_trans]
            ))%>%
  pivot_longer(cols=-household_id)%>%
  group_by(name) %>%
  mutate(value = factor(value,
                        levels = asset_labels[asset_labels$type=="fill_label", language_trans],
                        labels = asset_labels[asset_labels$type=="fill_label", language_trans]))%>%
  mutate(name = case_when(
    name == "transportation_own" ~ asset_labels[4,language_trans],
    name == "small_livestock_own" ~ asset_labels[5,language_trans],
    name == "small_consumer_own" ~ asset_labels[6,language_trans],
    name == "poultry_own" ~ asset_labels[7,language_trans],
    name == "other_land_own" ~ asset_labels[8,language_trans],
    name == "nonfarm_eqp_own" ~ asset_labels[9,language_trans],
    name == "non_mech_eqp_own" ~ asset_labels[10,language_trans],
    name == "mech_eqp_own" ~ asset_labels[11,language_trans],
    name == "large_consumer_own" ~ asset_labels[12,language_trans],
    name == "land_own" ~ asset_labels[13,language_trans],
    name == "house_own" ~ asset_labels[14,language_trans],
    name == "fish_pond_own" ~ asset_labels[15,language_trans],
    name == "cell_phone_own" ~ asset_labels[16,language_trans],
    name == "large_livestockown" ~ asset_labels[17,language_trans],
    .default = name
  ))%>%
  mutate(name = str_wrap(name,45))

assets%>%
  ggplot(aes(y = reorder(name,desc(name)), fill = reorder(value,desc(value))))+
  geom_bar(colour = "black", position = "fill")+
  labs(x = NULL,
       title = asset_labels[asset_labels$english=="Women's Household Asset Ownership", language_trans],
       y = NULL,
       fill = asset_labels[asset_labels$english=="Ownership status", language_trans])+
  theme_bw()+
  theme(legend.position = "bottom",
        legend.margin = margin(l = -.35, unit = "npc"))+
  scale_fill_manual(values = c("grey80", "#61958F", "#F39F5D"))+
  scale_x_continuous(labels = scales::percent)
```

```{r}
assets%>%
  ungroup()%>%
  group_by(name, value)%>%
  mutate(N = nrow(womens),
         n = n())%>%
  select(-household_id)%>%
  mutate(perc = n/N)%>%
  unique()%>%
  select(-N, -n)%>%
  pivot_wider(names_from = value, values_from = perc)%>%
  mutate_all(function(x) replace_na(x,0))%>%
  gt(groupname_col = NULL)%>%
  fmt_percent(columns = 2:4, decimals = 1)%>%
  cols_label(name = "Asset")
```


\pagebreak

## `r params$translations[params$translations$english=="PO.3 Household Income", language_trans]`

`r md(paste0("**",params$translations[params$translations$english=="Objective Definition", language_trans],"**"))` : `r params$translations[params$translations$element=="definition3", language_trans]`

### `r params$translations[params$translations$english=="Markets", language_trans]`

```{r, fig.width=9}
market_labels <- params$translations%>%filter(indicator=="Markets")

orangeblue <- colorRampPalette(c("#F39F5D","white","#61958F"))

colours <- orangeblue(7)

sales <- crops%>%
  select(label_lang,crop_use, crop_consumed_prop,crop_sold_prop)

# if(params$data_type == "processed"){
# 
# sales <- sales%>%
#   mutate(
#     crop_consumed_prop = ifelse(crop_use=="eat", "All", crop_consumed_prop),
#     crop_sold_prop = ifelse(crop_use=="sell", "All", crop_sold_prop)
#   )%>%
#   mutate_at(vars(crop_use:crop_sold_prop), function(x) ifelse(x == "","None", x))%>%
#   filter(crop_use!="None")%>%
#   mutate_at(vars(crop_consumed_prop, crop_sold_prop), function(x) factor(x,
#                                                                          levels = c("None","Little","UnderHalf","Half","Most","All"),
#                                                                          labels = market_labels[1:6,language_trans]))
# }

sales <- sales%>%
  group_by(label_lang)%>%
  mutate(n = n())%>%
  filter(n>5)

sales%>%
  mutate(label_lang = paste0(label_lang, " (n=",n,")"))%>%
  pivot_longer(cols = c(crop_consumed_prop, crop_sold_prop))%>%
  mutate(name = ifelse(name == "crop_sold_prop", market_labels[8,language_trans], market_labels[7,language_trans]))%>%
  ggplot(aes(y = reorder(label_lang,n),fill = value))+
  geom_bar(position = "fill", colour = "black")+
  facet_wrap(~name)+
  labs(x = NULL,
       y = market_labels[9,language_trans],
       fill = market_labels[10,language_trans])+
  scale_fill_manual(values = colours)+
  scale_x_continuous(labels = scales::percent)+
  theme_bw()+
  theme(legend.position = "top")+
  guides(fill = guide_legend(nrow=3))
```

```{r}
tbl1 <- sales%>%
  pivot_longer(cols = c(crop_consumed_prop, crop_sold_prop))%>%
  mutate(name = ifelse(name == "crop_sold_prop", market_labels[8,language_trans], market_labels[7,language_trans]))%>%
  filter(name == market_labels[7,language_trans])%>%
  mutate(label_lang = as.character(label_lang))%>%
  tbl_summary(
    include = value,
    by = label_lang,
    label = list(value = market_labels[7,language_trans])
  )

tbl2 <- sales%>%
  pivot_longer(cols = c(crop_consumed_prop, crop_sold_prop))%>%
  mutate(name = ifelse(name == "crop_sold_prop", market_labels[8,language_trans], market_labels[7,language_trans]))%>%
  filter(name == market_labels[8,language_trans])%>%
  mutate(label_lang = as.character(label_lang))%>%
  tbl_summary(
    include = value,
    by = label_lang,
    label = list(value = market_labels[8,language_trans])
  )

tbl_stack(list(tbl1,tbl2))%>%
  modify_header(label ~  "")
```


\pagebreak

### `r params$translations[params$translations$english=="Income Diversification", language_trans]`

`r md(paste0("**",params$translations[params$translations$english=="Diversity  & Importance of Income Sources", language_trans],"**"))`

```{r}
income_labels <- params$translations%>%
  filter(indicator=="I_HI_income_diversification")

indicators%>%
  tbl_summary(
    include = I_HI_income_diversification,
    label = I_HI_income_diversification~income_labels[12,language_trans]
  )
```

```{r}
off_farm%>%
    select(offfarm_income_name)%>%
  group_by(offfarm_income_name)%>%
  summarise(n = n(),
            N = nrow(global),
            perc  = n/N)%>%
  mutate(offfarm_income_name = factor(
    offfarm_income_name,
    levels = c("otherfarms","otherlabour","ownbusiness",
               "localbusiness","remittances", "gov_institution","other"),
    labels = income_labels[4:10,language_trans]
  ))%>%
  arrange(offfarm_income_name)%>%
  select(-N)%>%
  filter(!is.na(offfarm_income_name))%>%
  gt()%>%
  cols_label(
    offfarm_income_name = income_labels[12,language_trans],
    n = income_labels[13,language_trans],
    perc = "%"
  )%>%
  fmt_percent(3,decimals = 1)
```


### `r params$translations[params$translations$english=="Ability to Save & Pay Debts", language_trans]`

`r paste0(params$translations[params$translations$english=='Households reporting their financial situation as “We can buy everything we want and there is still money for potential savings”', language_trans], ": ", scales::percent(mean(indicators$I_HI_self_perception==levels(indicators$I_HI_self_perception)[1],na.rm=TRUE),accuracy = 0.1))`

`r paste0(params$translations[params$translations$english=="Does your household have any credit, debts or loans, or did you have any in the last 12 months?:", language_trans], " ", scales::percent(mean(indicators$I_HI_have_debt==1,na.rm=TRUE),accuracy = 0.1))`

`r paste0(params$translations[params$translations$english=="Did you ever find it difficult to pay the debts in the last 12 months", language_trans], ": ", scales::percent(mean(indicators$I_HI_worry_debt==1,na.rm=TRUE),accuracy = 0.1))`

\pagebreak

### `r params$translations[params$translations$english=="Self-Perception of Financial Situation", language_trans]`

```{r}
perception_labels <- params$translations%>%
  filter(indicator=="I_HI_self_perception")

perceptions <- indicators%>%
  filter(!is.na(I_HI_self_perception))

perceptions%>%
  tbl_summary(
    include = I_HI_self_perception,
    label = list(I_HI_self_perception ~ perception_labels[8,language_trans])
  )%>%
  modify_header(label ~  "")
```

\pagebreak

## `r params$translations[params$translations$english=="PO.4 Food Security & Dietary Diversity", language_trans]`

`r md(paste0("**",params$translations[params$translations$english=="Objective Definition", language_trans],"**"))` : `r params$translations[params$translations$element=="definition4", language_trans]`

### `r params$translations[params$translations$english=="Household Dietary Diversity", language_trans]`

`r language_switch(language = language_trans, element_name = "extra_text1", language_file = params$translations)`

`r language_switch(language = language_trans, element_name = "extra_text2", language_file = params$translations)`

`r paste0(params$translations[params$translations$english=="% Households Reached minimum level of diversity (at least 5 food groups):", language_trans], " ", scales::percent(mean(indicators$I_HDDS_min,na.rm=TRUE),accuracy = 0.1))`

```{r}
indicators%>%
  mutate(I_HDDS = factor(I_HDDS, levels = c(0:12), labels = c(0:12)))%>%
  filter(!is.na(I_HDDS))%>%
  group_by(I_HDDS, .drop = FALSE)%>%
  summarise(n = n())%>%
  ggplot(aes(x = I_HDDS, y = n))+
  geom_col(fill = "#61958F", colour = "black")+
  geom_label(aes(label = n))+
  labs(x = params$translations[params$translations$english=="Household Dietary Diversity Score", language_trans],
       y =params$translations[params$translations$english=="Number of Households", language_trans][1])+
  theme_bw()
```

\pagebreak

### `r params$translations[params$translations$english=="FIES (Food Insecurity)", language_trans]`

`r language_switch(language = language_trans, element_name = "extra_text3", language_file = params$translations)`

`r language_switch(language = language_trans, element_name = "extra_text4", language_file = params$translations)`

* `r language_switch(language = language_trans, element_name = "extra_text5", language_file = params$translations)`
* `r language_switch(language = language_trans, element_name = "extra_text6", language_file = params$translations)`
* `r language_switch(language = language_trans, element_name = "extra_text7", language_file = params$translations)`
* `r language_switch(language = language_trans, element_name = "extra_text8", language_file = params$translations)`

`r paste0(params$translations[params$translations$english=="Estimated % of households with moderate or severe food insecurity", language_trans], ": ", scales::percent(mean(indicators$I_FIES_prev_moderate,na.rm=TRUE),accuracy = 0.1))`

`r paste0(params$translations[params$translations$english=="Estimated % of households with severe food insecurity", language_trans], ": ", scales::percent(mean(indicators$I_FIES_prev_severe,na.rm=TRUE),accuracy = 0.1))`


```{r}
fies_cat_labs <- params$translations%>%
  filter(indicator == "I_FIES_category" & type=="label")

fies_cats <- indicators %>%
  mutate(N = n()) %>%
  group_by(I_FIES_category) %>%
  summarise(N = mean(N), n = n(), `%` = n / N) %>% 
  select(-N)

fies_cats%>%
  gt()%>%
  fmt_percent(columns = 3, decimals = 1) %>%
  cols_label(I_FIES_category = params$translations[params$translations$english ==
                                                     "FIES Category", language_trans]) #%>%
  # tab_footnote(footnote = params$translations[params$translations$english ==
  #                                               "All FIES Qs = 'No'", language_trans],
  #              locations = cells_body(columns = 1, rows = 1)) %>%
  # tab_footnote(footnote = params$translations[params$translations$english ==
  #                                               "FIES Q5- Q8 = 'No'", language_trans],
  #              locations = cells_body(columns = 1, rows = 2)) %>%
  # tab_footnote(footnote = params$translations[params$translations$english ==
  #                                               "FIES Q5 or Q6 or Q7 = 'Yes'", language_trans],
  #              locations = cells_body(columns = 1, rows = 3)) %>%
  # tab_footnote(footnote = params$translations[params$translations$english ==
  #                                               "FIES Q8 = 'Yes'", language_trans],
  #              locations = cells_body(columns = 1, rows = 4))
```


```{r}
indicators%>%
  group_by(I_FIES_score)%>%
  summarise(n = n())%>%
  ggplot(aes(x = I_FIES_score, y = n))+
  geom_col(fill = "#61958F", colour = "black")+
  geom_label(aes(label = n))+
  scale_x_continuous(n.breaks = 8)+
  labs(x = params$translations[params$translations$english=="FIES Score", language_trans],
       y = params$translations[params$translations$english=="Number of Households", language_trans][1])+
  theme_bw()
```

```{r}
fies_labels <- params$translations%>%
  filter(indicator=="FIES")

indicators%>%
  select(household_id, FIES_1:FIES_8)%>%
  pivot_longer(cols=-household_id)%>%
  group_by(name) %>%
  summarise(
    N = sum(!is.na(value)),
    n = sum(value,na.rm = TRUE),
    perc = n/N
  )%>%
  mutate(name = factor(name,
    levels = c("FIES_1", "FIES_2","FIES_3", "FIES_4",
               "FIES_5", "FIES_6","FIES_7", "FIES_8"),
    labels = fies_labels[5:12,language_trans]))%>%
  ggplot(aes(y = reorder(name,desc(name)), x = perc))+
  geom_col(fill = "#61958F", colour = "black")+
  geom_label(aes(label = scales::percent(perc,accuracy = 0.1)))+
  scale_x_continuous(labels = scales::percent, limits = c(0,1))+
  labs(x = NULL,
       title = str_wrap(fies_labels[13,language_trans],40),
       y = NULL)+
  theme_bw()
```

```{r, results = 'asis'}
if("Agric_Inputs"%in%global_form$name){
cat('\\pagebreak')
}
```


### `r ifelse("Agric_Inputs"%in%global_form$name,params$translations[params$translations$english=="Agricultural Inputs and Practices", language_trans], '')`

```{r}
form_lang <- paste0("choices_", language_trans)
global_form$choices_lang <- global_form[[form_lang]]

if("Agric_Inputs"%in%global_form$name){
multi_table(global, global_form, "Agric_Inputs", filter_crop = TRUE,language = language_trans, language_file = params$translations)%>%
  modify_header(label ~  
                  md(paste0("**",params$translations[params$translations$english=="Agricultural Inputs",
                                              language_trans],"**")))
}
```

```{r}
if("Irrigation_method"%in%global_form$name){
multi_table(global, global_form, "Irrigation_method",filter_crop = TRUE,language = language_trans, language_file = params$translations)%>%
  modify_header(label ~  
                  md(paste0("**",params$translations[params$translations$english=="Irrigation Methods",
                                              language_trans],"**")))
}
```

```{r}
if("tree_uses"%in%global_form$name){
multi_table(global, global_form, "tree_uses",filter_crop = TRUE,language = language_trans, language_file = params$translations)%>%
  modify_header(label ~  
                  md(paste0("**",params$translations[params$translations$english=="Tree usage",
                                              language_trans],"**")))
}
```

\pagebreak

```{r}
if("tillage_power"%in%global_form$name){
multi_table(global, global_form, "tillage_power",filter_crop = TRUE,language = language_trans, language_file = params$translations)%>%
  modify_header(label ~  
                  md(paste0("**",params$translations[params$translations$english=="Tillage Power",
                                              language_trans],"**")))
}
```

```{r}
if("water_cons_practices"%in%global_form$name){
multi_table(global, global_form, "water_cons_practices",filter_crop = TRUE,language = language_trans, language_file = params$translations)%>%
  modify_header(label ~  
                  md(paste0("**",params$translations[params$translations$english=="Water Conservation Practices",
                                              language_trans],"**")))
}
```

```{r}
if("Livestock_Medicines"%in%global_form$name){
multi_table(global, global_form, "Livestock_Medicines", filter_livestock = TRUE,language = language_trans, language_file = params$translations)%>%
  modify_header(label ~  
                  md(paste0("**",params$translations[params$translations$english=="Livestock Medicines",
                                              language_trans],"**")))
}
```

